---
title: "Reproducing the benchmark"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Reproducing the benchmark}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", eval = FALSE)
```

The package ships the full bench harness used in Jakel (2026): 14 of the
FFTrees-bundled datasets × 20 stratified 70/30 splits × all runners.

## Datasets

```{r}
library(adaptiveFFT)
FFT_DATASETS
```

## One full run

The driver script lives at `inst/bench/run_full_bench.R`:

```{r}
script <- system.file("bench", "run_full_bench.R", package = "adaptiveFFT")
file.show(script)
# source(script)   # ~3-4 hours on a single core
```

Output is appended to `inst/bench/results/baseline_bench.fst` as a long
`data.table`:

```
dataset, seed_idx, runner, acc, bacc, f1, auc, frugality, train_time,
n_test, n_pos_test, notes
```

## Pre-computed results

For convenience, the FST containing all 5,824 rows of the published bench
is included at `inst/bench/results/baseline_bench.fst`:

```{r}
res <- fst::read_fst(
  system.file("bench", "results", "baseline_bench.fst", package = "adaptiveFFT"))
str(res)
```

## Headline numbers (paper Table 1)

```{r}
library(data.table)
dt <- as.data.table(res)
dt[seed_idx <= 20L,
   .(mean_bacc = round(mean(bacc, na.rm = TRUE), 3),
     n         = .N),
   by = runner][order(-mean_bacc)]
```

## Statistical tests

The dataset-level Wilcoxon signed-rank + rank-biserial effect-size
analysis used in the paper is reproduced by `inst/bench/make_stats.R`:

```{r}
source(system.file("bench", "make_stats.R", package = "adaptiveFFT"))
```
