---
title: "Quickstart: fitting an adaptive FFT"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Quickstart: fitting an adaptive FFT}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment  = "#>",
  fig.width  = 9,
  fig.height = 8
)
set.seed(2026)
```

`adaptiveFFT` fits chain Fast-and-Frugal Trees (depth ≤ 4, one cue per
node, binary exits) and additionally races two FFT families on an inner
holdout to pick the better one for each dataset.

## Load a dataset and split

```{r}
library(adaptiveFFT)

d <- load_fft_dataset("heartdisease")
in_tr <- make_split(d$y, seed = 2026L + 1001L)
tr <- d[in_tr]; te <- d[!in_tr]
nrow(tr); nrow(te)
```

## Fit and inspect

```{r}
fit <- adaptive_fft(tr, te, dataset_name = "heartdisease",
                    baselines = list(`ifan (paper)` = 0.787))
print(fit)
```

`fit$winner` is whichever family won the inner race; `fit$chain` shows the
predicate sequence of the winning tree.

## Plot

The default `plot()` renders a 4-panel figure mirroring FFTrees' visual
grammar — tree with side icon arrays, confusion matrix, test metrics, and
Δ-vs-baseline plot:

```{r, eval = FALSE}
plot(fit)
```

You can request individual panels:

```{r, eval = FALSE}
plot(fit, what = "tree")
plot(fit, what = "perf")
```

Or save publication-ready output:

```{r, eval = FALSE}
plot(fit, save_to = "fig_demo")  # writes fig_demo.{pdf,png}
```

## Standalone beam search

If you only want the chain-FFT search without the inner race:

```{r, eval = FALSE}
r <- run_beam_fft(tr, te, max_levels = 4L, beam_B = 10L,
                  max_thresholds_per_cue = 5L, item_cap = 50L)
m_bacc(te$y, r$pred)
```

## Reproduce the paper's benchmark

The bundled benchmark script reproduces the 14 datasets × 20 seeds grid:

```{r, eval = FALSE}
system.file("bench", "run_full_bench.R", package = "adaptiveFFT")
```

See the `Benchmarking` vignette for details.
